---
title: "Telco Churn Data Cleaning"
author: "Koby Sokoloff"
date: "September 11, 2018"
output: html_document
---

Import all the necessary packages.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(plyr)
library(tidyverse)
```

## Import the dataset

Read in the dataset and check its structure.
```{r cars}
churn <- read.csv('Telco-Customer-Churn.csv')
#str(churn)
```


## Clean the dataset

Check to see the number of missing values per column.
```{r}
sapply(churn, function(x) sum(is.na(x)))
```

Remove all rows with missing values.
```{r}
churn <- churn[complete.cases(churn), ]
```

Change 6 columns from "No internet Service" to "No". 
```{r}
cols_recode1 <- c(10:15)
for (i in 1:ncol(churn[,cols_recode1])) {
  churn[,cols_recode1][,i] <- as.factor(mapvalues 
                                        (churn[,cols_recode1][,i], 
                                         from=c("No internet service"),to=c("No")))
}
```

Change "No phone service" to "No" for column 'MultipleLine'
```{r}
churn$MultipleLines <- as.factor(mapvalues(churn$MultipleLines,
                                           from=c("No phone service"),
                                           to=c("No")))
```

Created a new column bucketing customer tenure into groups.
```{r}
group_tenure <- function(tenure) {
  if (tenure >= 0 & tenure <= 12) {
    return ('0-12 Months')
  } else if (tenure > 12 & tenure <= 24) {
    return ('12-24 Months')
  } else if (tenure > 24 & tenure <= 36) {
    return ('24-364 Months')
  } else if (tenure > 36 & tenure <= 48) {
    return ('36-48 Months')
  } else if (tenure > 48 & tenure <= 60) {
    return ('48-60 Months')
  } else if (tenure > 60) {
    return ('> 60 Months')
  }
}

churn$TenureGroup <- sapply(churn$tenure,group_tenure)
churn$TenureGroup <- as.factor(churn$TenureGroup)
```

Changing values of 'Senior Citizen' from "0" or "1" to "No" or "Yes"
```{r}
churn$SeniorCitizen <- as.factor(mapvalues(churn$SeniorCitizen,
                                           from=c("0","1"),
                                           to=c("No","Yes")))
```

Remove columns not needed for analysis.
```{r}
churn$customerID <- NULL
churn$tenure <- NULL
churn$Gender <- churn$gender
churn$gender <-NULL
head(churn)
```

## Export the cleaned data to excel

Export churn dataframe back to excel.
```{r}
write.csv(churn, file = "telcoData.csv") 
```
